---
title: "WorldPhones 
        Data Product Pitch"
date: 2016, 26 November
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## WordPhones
WordPhones is a dataset included in R by default. It provides information about phone distributions along different regions. 
```{r , echo = FALSE}
head(WorldPhones,n=2)
```
The proposed app use the data for each region through a diversity of year to fit a basic
linear model with the objective to predict the number of phones in future years

The application does not require any special requirement of imports from the user computer

## Available tabs: Documentation
The app is documenting covering three aspects:

* An introduction to the data set that has been used
* How the application should be used
* The technical details of the application

## Available tabs: Regresion
In this tab will be plotted the result of the model with the fitted line covering the regression line
```{r , echo = FALSE, comment=""}
years <- c(1951,1956,1957,1958,1959,1960,1961)
model<-lm(WorldPhones[ ,"Europe"] ~ years)
plot(WorldPhones[ ,"Europe"] ~ years, xlab = "years for Europe", ylab = "Phones in Europe",main = "Regression Phones vs Years for: Europe")
abline(model)
```

Additionally, The tab printed the results the model foreseen for the selected year 

## Conclusions
The app is a simple application for regression and prediction, using reactive programming and interactivity with the user. This interactivity allows the user to control, both the resultand the presentation.

*Presentation*: There are three checks that controls the printing of the title, and the x,y legends. The checkboxes allow the user to select if the legends will appear

*Behavior*: The fit of the model is done in each case, but the selection of the region determine the data to be used. The user may select if a prediction is rquired and the year for that prediction for the selected region. For instance,for Europe, year 2000:

```{r , echo = FALSE, comment=""}
prediction <- model$coefficients[1]+model$coefficients[2]*2000
prediction
```



